### 2023-12-21 options/symbols_and_cmd.tex
Drop Chapter on case_study
From atom_vs_molecule paper

%% P
\newabbreviation[group={Acronyms}]{PCE}{PCE}{Polynomial Chaos Expansion}

%% S
\newabbreviation[group={Acronyms}]{SDGs}{SDGs}{Sustainable Development Goals}

@@

%------------------------
%% E
\newcommand{\etal}{\textit{et~al.}}
\newcommand{\eg}{e.g.\ }

@@

%------------------------
%% I
\newcommand{\ie}{i.e.\ }

@@

%------------------------
%% X
\newcommand{\xv}{\mathbf{x}}
\newcommand{\xb}{\boldsymbol{x}}

>>>>

%% B
\newabbreviation[group={Acronyms}]{BEV}{BEV}{battery electric vehicle}

%% C
\newabbreviation[group={Acronyms}]{CCGT}{CCGT}{combined cycle gas turbine}

%% D
\newabbreviation[group={Acronyms}]{DHN}{DHN}{district heating network}

%% E
\newabbreviation[group={Acronyms}]{EUD}{EUD}{end-use demand}

%% F
\newabbreviation[group={Acronyms}]{FC}{FC}{fuel cell}

%% G
\newabbreviation[group={Acronyms}]{GWP}{GWP}{global warming potential}

%% H
\newabbreviation[group={Acronyms}]{HP}{HP}{heat pump}
\newabbreviation[group={Acronyms}]{HVC}{HVC}{high value chemicals}

%% L
\newabbreviation[group={Acronyms}]{LCOE}{LCOE}{levelised cost of energy}

%% N
\newabbreviation[group={Acronyms}]{NED}{NED}{non-energy demand}

%% P
\newabbreviation[group={Acronyms}]{PCE}{PCE}{Polynomial Chaos Expansion}
\newabbreviation[group={Acronyms}]{PV}{PV}{photovoltaic}

%% S
\newabbreviation[group={Acronyms}]{SDGs}{SDGs}{Sustainable Development Goals}
\newabbreviation[group={Acronyms}]{SMR}{SMR}{small modular reactor}

@@

%------------------------
%% E
\newcommand{\etal}{\textit{et~al.}}

@@

%------------------------
%% I

@@

%------------------------
%% X
\newcommand{\xv}{\mathbf{x}}
\newcommand{\xb}{\boldsymbol{x}}
\newcommand{\xmark}{\ding{55}}
